Imputation of Incomplete Multilevel Data with R

### 2024-01-16 Manuscript/manuscript.qmd
edits background

<!-- I don't understand the following paragraph. What is meant with "is restricted in datasets..."? -->
Regarding the restrictions imposed by the data, for instance, the use of cluster indicator variables is restricted in datasets where there are not many clusters and many observations per cluster (Graham, 2009). The last restriction is also required when imputations are performed on each cluster separately.  When this restriction cannot be achieved, one can use an imputation model that simultaneously imputes all clusters using a hierarchical model (Allison 2002).

@@

@@

In a hierarchical imputation model, random effects model the correlations between observations within clusters, making it possible to estimate even with a small number of observations per cluster. There are various proposed multiple imputation models based on hierarchical models, each with its own set of assumptions \cite{audigier}.

>>>>

<!-- I don't understand the following paragraph. What is meant with "is restricted in datasets..."? -->
<!-- Also, this info is also mentioned in ##### Clustering Inclusion -->
Regarding the restrictions imposed by the data, for instance, the use of cluster indicator variables is restricted in datasets where there are not many clusters and many observations per cluster (Graham, 2009). The last restriction is also required when imputations are performed on each cluster separately.  When this restriction cannot be achieved, one can use an imputation model that simultaneously imputes all clusters using a hierarchical model (Allison 2002).

@@

<!-- most of this subsection is also mentioned at the start of #sec-workflow -->

@@

In a hierarchical imputation model, random intercepts and random effects model the correlations between observations within clusters, making it possible to estimate even with a small number of observations per cluster. There are various proposed multiple imputation models based on hierarchical models, each with its own set of assumptions \cite{audigier}.
